\section{Methodology}
\subsection{Introduction}
In this  Section  i will discuss the  proposed  methodology of this  project this will cover the  following:
\begin{enumerate}
    \item The Research Philosophy
    \item The Research Approach
    \item The Research Design
    \item The Data Collection Methods
    \item The Model Development
    \item The Data Analysis Methods
    \item The Ethical Considerations
    \item The validity and reliability 
    \item The Limitations and Delimitation
    \item The timeline
\end{enumerate} 
\subsection{Research Philosophy}

This research adopts a pragmatic philosophy, which emphasizes the practical application of knowledge and the need for researchers to be flexible and adaptable in their approaches. This aligns well with the computational nature of the research, as it allows for the exploration of different methods and techniques to achieve the research goals.

\subsection{Research Approach}

This study employs a computational research approach, which involves the development and utilization of software tools and algorithms to address research questions. Computational methods are well-suited for handling large datasets, complex systems, and experimental simulations.

\subsection{Research Design}

\subsection{Data Collection Methods}
In this section  i dicuss the  following:
\begin{enumerate}
    \item the  intall  unit test this is for  what we  expect  our  sensor  to  output this  will  be  updated
    \item How  the data  from sensor will be stored 
    \item the code  assoicated   with the above points 
\end{enumerate}
\subsubsection{Unit testing}
Fristly i want to made  some unit tests the aim of this  is the  following:
\begin{itemize}
    \item To make  test  that will be  there for  the  codeing  section of  the  project 
\end{itemize}
this section will discuss the  following for  testing:
\begin{enumerate}
    \item 1 x DHT22
    \item 1 x DFR0026
    \item 1 x AS312
    \item 1 x MM2 Series 900 MHz
    \item 1 x MCP3008
    \item 1 x Raspberry Pi VR 220 Camera
    \item  1 x Li-polymer Battery HAT 
    \item 1 x Turbo 1GB 
\end{enumerate}
\subsubsection{DHT22}
According to the  data sheet \cite{sparkfun} seen as  the data is   8 bits  and  the  range at which this   operates at  -40 to 80$^{o}$c for tempeature
meaning we have  at least  7 bit in the  exponent to  represent  the   measured value.
to represent  the  high  end of this  sensor i used the  following calculation:
$$ 2^6 +2^4 = 80$$ which mean  we have  a 2 bits dedicated to decimal place so the  high temperature to be 80.3$^{o}$c
for the  lowest temp we have 6 bits  to  represent  - 40 due to  2s complement  so lowest  will   be -40.3$^{o}C$
so with that  that  stablish we  must  make a  unit  that will do  the  following:
\begin{enumerate}
    \item Test if the  output is  a float
    \item Test the  high end of  the  temp sensor so it  reads  80.3 as  the highest
    \item Test for the  lowest   temp   around 
\end{enumerate}
be sure to follow  steps  for  folder  setup  follow instructions on page \pageref{folderstructure}.
we get the following sample code:
\begin{lstlisting}[style=mystyle,caption={sample test intial code}]
import unittest
from protest import Read_DHT22
class test_project_code(unittest.TestCase):
    def test_DHT_22_temp_output_type(self):
        self.assertIsInstance(Read_DHT22, float)
    def test_DHT22_temp_range(self):
        self.assertGreaterEqual(Read_DHT22,-30.3)
        self.assertLessEqual(Read_DHT22,80.3)
    
\end{lstlisting} 
for  humidity  the Datasheet which ranges from 0 to 100 \%
we want to test for the following:
\begin{enumerate}
    \item Test if the  output is  a float
    \item Test if the  output ranges 0 to 100
\end{enumerate}
this lead to the  following code 
\begin{lstlisting}[style=mystyle,caption={sample test for DHT22}]
import unittest
from protest import Read_DHT22
class test_project_code(unittest.TestCase):
    hum,temp=Read_DHT22(2)
    def test_DHT22_output_type(self):
        self.assertIsInstance(Read_DHT22,tuple)
    #....

    def test_DHT22_hum_output_type(self):
        self.assertIsInstance(hum,float)

    def test_DHT22_hum_range(self):
        self.assertGreaterEqual(hum,0.0)
        self.assertLessEqual(hum,100.0)
\end{lstlisting}
\subsubsection{DFR0026 \& MCP3008}
According to the  datasheet \cite{ada} we must keep in mind  that this  componet is  connected to  an ADC 
this  will  give  me  the  following  test conditions:
\begin{enumerate}
    \item Test if  the output is a float

    \item Test  the  range of this  with the  upper limit being 5v 
    \item test the  lover limit being 0 
\end{enumerate}
\begin{lstlisting}[style=mystyle,caption={unit test for  DFR0026 and  MCP3008}]
    import unittest
    from protest import Read_DHT22,Read_MCP3008
    class test_project_code(unittest.TestCase):
    def test_DFR0026_MCP3008_out_type(self):
        self.assertIsInstance(Read_MCP3008,float)
    def test_DFR0026_MCP3008_out_range(self):
        self.assertLessEqual(5.0000000)
        self.assertGreaterEqual(0.0000000)
\end{lstlisting}
\subsubsection{AS312}
for  this section  we  want our  tests  to  be  the following:
\begin{enumerate}
    \item test for type is boolean 
\end{enumerate}
we can  now add to the snipppet :
\begin{lstlisting}
    def test_AS312_out_type(self):
        self.assertIsInstance(Read_AS312,bool)
\end{lstlisting}
\textbf{Note : Don't forget to import read_as12 function from test file}

\subsubsection{Raspberry Pi VR 220 Camera}
according to the  data sheet \cite{Camera}
we the  resoultion to  it uses is  1080p50 which is 1920x1080p so our  tests will have to  in copoarte  the  followoing:
\begin{enumerate}
    \item Test the  output shape  if open cv is  gonna  be  used 
    \begin{enumerate}
        \item test  the  amout of   elelecelm in the  3 dimesional   array 
    \end{enumerate}
    \item test the  file  type  is png
\end{enumerate}
this would lead me to the following code snippet.
\begin{lstlisting}
    def test_Raspberry_Pi_VR220_out_shape(self):
    self.assertEqual(Read_Raspberry_PiVR220.shape,(1920,1080,3))
\end{lstlisting}
\subsubsection{Li-polymer Battery HAT}

\subsubsection{Turbo 1GB }

\subsubsection{MM2 Series 900 MHz}

\subsubsection{conculsion}
The  intiall  draft  code  for  the  test  devlopemnt  si the  following
\begin{lstlisting}[style=mystyle,caption={Final draft test template}]
    # waiting for other sections 
\end{lstlisting}

\subsection{Model Development}

High-performance computing (HPC) resources are utilized to develop and train computational models. The models are designed to capture the essential features of the research problem and generate meaningful outputs.

\subsection{Data Analysis Methods}

Statistical and machine learning techniques are employed to analyze the data collected from both computational models and real-world sources. These techniques are used to identify patterns, trends, and relationships within the data.

\subsection{Ethical Considerations}

The use of computational methods raises ethical concerns regarding data privacy and security. To address these concerns, data anonymization and encryption techniques are employed to protect sensitive information. Additionally, informed consent is obtained from participants when applicable.

\subsection{Validity and Reliability}

Validation of computational models is achieved through rigorous testing and evaluation. This involves comparing model predictions with real-world data and examining the sensitivity of the models to different parameters. Reliability is ensured through the use of standardized methods and procedures for data collection, analysis, and interpretation.

\subsection{Limitations and Delimitations}

The computational nature of the research introduces limitations due to the complexity of the systems being modeled and the potential for errors in modeling and data analysis. Moreover, the generalizability of the findings may be limited to the specific contexts and conditions considered in the research.

\subsection{Timeline}

The model development phase of the research is scheduled to take place from [start date] to [end date]. The data collection and analysis phases are scheduled to take place from [start date] to [end date]. The final write-up of the research is scheduled to be completed by [deadline date].